Marlowe: financial contracts on blockchain\thanks{This work is part of the Cardano project and is supported by IOHK,~\url{https://iohk.io}}

### 2018-07-18 tex/paper.tex
Expand comparison in related work

Stand-alone DSLs have the advantage of providing appropriate, domain-level error messages when things go wrong, but 
suffer the disadvantage of having to be implemented from scratch. An alternative to this are \emph{embedded} DSLs 
(EDSLs), which provide a ``little language'' for the particular domain embedded within a general-purpose host language. 
This means that parts of the host -- such as arithmetical expressions, or list idioms --  can be used to extend the 
expressibility of the DSL. A notable example of this is the financial contracts language described by Peyton Jones and 
his collaborators~\cite{PeytonJones:2000}, which is embedded in Haskell.

>>>>

Stand-alone DSLs have the advantage of providing appropriate, domain-level error messages when things go wrong, but 
suffer the disadvantage of having to be implemented from scratch. An alternative to this are \emph{embedded} DSLs 
(EDSLs), which provide a ``little language'' for the particular domain embedded within a general-purpose host language. 
This means that parts of the host -- such as arithmetical expressions, or list idioms --  can be used to extend the 
expressibility of the DSL. A notable example of this is the financial contracts language described by Peyton Jones and 
his collaborators~\cite{PeytonJones:2000}, which is embedded in Haskell. Marlowe is similar to the 
DSL in~\cite{PeytonJones:2000} in the use of Haskell embedding, in that the functionality provided is similar, in the use of 
composable combinators, and in the declarative style that allows users to describe what needs to be enforced and not how. 
However the two approaches differ in other aspects like the lack of Marlowe's reliance on the legal system for 
enforcement, its support for multiple party contracts, its explicitness of choices, and its use of a pull model.
